\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-23 icse/eval.tex
Updated evaluation

\begin{figure}[t]
  \[
    \begin{array}{c?r|r|r|r|r?r}
      \textbf{Version}
      & \multicolumn{1}{c|}{\textbf{2016}}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c|}{\textbf{2019}}
      & \multicolumn{1}{c?}{\textbf{2020}}
      & \multicolumn{1}{c}{\textbf{avg.}}\\\toprule
      \text{\# Lexical prod.}
      & \text{78}
      & \text{78}
      & \text{78}
      & \text{81}
      & \text{81}
      & \text{79.2}\\\hline
      \text{\# Syntactic prod.}
      & \text{157}
      & \text{167}
      & \text{167}
      & \text{174}
      & \text{175}
      & \text{168}\\
    \end{array}
  \]
  \[
    \begin{array}{c|r|r|r|r?r}
      \textbf{Old version}
      & \multicolumn{1}{c|}{\textbf{2016}}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c?}{\textbf{2019}}
      & \multirow{2}{*}{\textbf{avg.}}\\\cline{1-5}
      \textbf{New version}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c|}{\textbf{2019}}
      & \multicolumn{1}{c?}{\textbf{2020}}
      & \\\toprule
      \Delta \; \text{\# Lexical prod.}
      & \text{3}
      & \text{5}
      & \text{6}
      & \text{0}
      & \text{4.7}\\\hline
      \Delta \; \text{\# Syntactic prod.}
      & \text{140}
      & \text{15}
      & \text{8}
      & \text{2}
      & \text{55}\\
    \end{array}
  \]
  \caption{Number of productions in specifications,
from \textit{all} of which \( \tool \) automatically generated parsers}
  \label{fig:syntax-all-version}
\end{figure}

\begin{figure}[t]
  \centering
  \begin{subfigure}{0.23\textwidth}
    \includegraphics[width=\textwidth]{img/all-version-sem.png}
    \caption{Results for different versions}
    \label{fig:semantics-all-version}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.20\textwidth}
    \includegraphics[width=\textwidth]{img/all-version-sem-delta.png}
    \caption{Results for differences between versions}
    \label{fig:semantics-all-version-delta}
  \end{subfigure}
  \caption{Number of abstract algorithms in specifications, from which
\( \tool \) generated the JavaScript semantics}
  \label{fig:all-version}
\end{figure}

We evaluate the effectiveness of \( \tool \) by applying it to the
most recent five versions of the ECMAScript specifications, ECMAScript
2016 to 2020.  We measured for how many grammar productions and
abstract algorithms \( \tool \) automatically generates parsers and
semantics, respectively, in two respects: 1) in each version and 2) in
each difference between adjacent versions.

For syntax, we measured the number of grammar productions for which
\textsf{Parser Generator} automatically generated parsers.  As summarized in
Figure~\ref{fig:syntax-all-version}, the average numbers of lexical and
syntactic grammar productions are \inred{XX} and \inred{XXX}, respectively.
In addition, the average numbers of annually updated lexical and
syntactic grammar productions between adjacent versions are \inred{X}
and \inred{XX}, respectively.  We report that \( \tool \)
automatically generated parsers for \textit{all} the productions.

For semantics, we measured the number of abstract algorithms that
\textsf{Algorithm Compiler} with the compile rules described in
Section~\ref{sec:impl} automatically covered.
Figure~\ref{fig:all-version} shows that \( \tool \) could
automatically extract semantics with the \inred{XX\%} success rate on
average for existing specifications, and \inred{XX\%} for changed or
newly defined algorithms.  Thus, we believe that \( \tool \) effectively
reduces the efforts to extract the syntax and semantics of JavaScript
not only for developing them from scratch, but also for updating
existing ones.

>>>>

\begin{table}[t]
  \caption{Number of productions in specifications,
from \textit{all} of which \( \tool \) automatically generated parsers}
  \label{fig:syntax-all-version}
  \[
    \begin{array}{c?r|r|r|r|r?r}
      \textbf{Version}
      & \multicolumn{1}{c|}{\textbf{2016}}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c|}{\textbf{2019}}
      & \multicolumn{1}{c?}{\textbf{2020}}
      & \multicolumn{1}{c}{\textbf{avg.}}\\\toprule
      \text{\# Lexical prod.}
      & \text{78}
      & \text{78}
      & \text{78}
      & \text{81}
      & \text{81}
      & \text{79.2}\\\hline
      \text{\# Syntactic prod.}
      & \text{157}
      & \text{167}
      & \text{167}
      & \text{174}
      & \text{175}
      & \text{168}\\
    \end{array}
  \]
  \[
    \begin{array}{c|r|r|r|r?r}
      \textbf{Old version}
      & \multicolumn{1}{c|}{\textbf{2016}}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c?}{\textbf{2019}}
      & \multirow{2}{*}{\textbf{avg.}}\\\cline{1-5}
      \textbf{New version}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c|}{\textbf{2019}}
      & \multicolumn{1}{c?}{\textbf{2020}}
      & \\\toprule
      \Delta \; \text{\# Lexical prod.}
      & \text{3}
      & \text{5}
      & \text{6}
      & \text{0}
      & \text{4.7}\\\hline
      \Delta \; \text{\# Syntactic prod.}
      & \text{140}
      & \text{15}
      & \text{8}
      & \text{2}
      & \text{55}\\
    \end{array}
  \]
\end{table}

\begin{figure}[t]
  \centering
  \begin{subfigure}{0.46\textwidth}
    \includegraphics[width=\textwidth]{img/sem-all.png}
    \caption{Results for existing versions}
    \label{fig:semantics-all-version}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{img/sem-delta.png}
    \caption{Results for differences between adjacent versions}
    \label{fig:semantics-all-version-delta}
  \end{subfigure}
  \caption{Number of steps for abstract algorithms in specifications, from which
\( \tool \) generated the JavaScript semantics}
  \label{fig:all-version}
\end{figure}

We evaluate the effectiveness of \( \tool \) by applying it to the
most recent five versions of the ECMAScript specifications, ECMAScript
2016 to 2020.  We measured for how many grammar productions and
steps in abstract algorithms \( \tool \) automatically generates parsers and
semantics, respectively, in two respects: 1) in each version and 2) in
each difference between adjacent versions.

For syntax, we measured the number of grammar productions for which
\textsf{Parser Generator} automatically generated parsers.  As summarized in
Figure~\ref{fig:syntax-all-version}, the average numbers of lexical and
syntactic grammar productions are 79.2 and 168, respectively.
In addition, the average numbers of annually updated lexical and
syntactic grammar productions between adjacent versions are 4.7
and 55, respectively.  We report that \( \tool \)
automatically generated parsers for \textit{all} the productions.

For semantics, we measured the number of steps in abstract algorithms that
\textsf{Algorithm Compiler} with the compile rules described in
Section~\ref{sec:impl} automatically covered.
Figure~\ref{fig:all-version} shows that \( \tool \) could
automatically extract semantics with the 91.60\% success rate on
average for existing specifications, and 90.43\% for changed or
newly defined steps.  Moreover, we found that algorithm steps in
built-in libraries are less covered than other language semantics
with 86.98\% success rates (86.09\% for updates).
It is due to the diverse writing styles to represent
their own specific functionalities.
However, steps in core language semantics are covered
with higher success rates 95.35\% (95.25\% for updates).

According to this evaluation, we believe that \( \tool \) effectively
reduces the efforts to extract the syntax and semantics of JavaScript
not only for developing them from scratch, but also for updating
existing ones.
